---
title: "NMR Data Analysis Tutorial"
author: "Nightingale Health Ltd."
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Blood Biomarker Analysis Tutorial}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>", 
  fig.width = 7, 
  fig.height = 7, 
  fig.align = "center")
library(tidyverse)
library(ggforestplot)
```

## Overview

In this tutorial we will go through the basic steps of importing blood metabolomics 
data into R, joining them with phenotypes or endpoint data, and performing basic 
epidemiological analysis. The tutorial uses simulated demo datasets from
[Nightingale's NMR platform](https://nightingalehealth.com/technology).

## Prerequisites

This tutorial uses R, which is free, compiles and runs in most operating 
systems. If you don't have it already installed in your system, you may install 
it by following the instructions [here](https://www.r-project.org/). Additionally, 
we recommend using the RStudio IDE (Integrated Development Environment), 
which can be downloaded and installed following the instructions 
[here](https://www.rstudio.com/products/rstudio/download/) 
for the free "RStudio Desktop (Open Source License)".

You should be able to reproduce easily the code in this tutorial, even with 
very little knowledge in programming. If you have never programmed in R before
and are intrested to learn more, you may find the following book useful, 
[Hands on Programming with R](https://rstudio-education.github.io/hopr/) by 
Garrett Grolemund.

Throughout the tutorial, we will be using the collection of 
[`tidyverse` R packages](https://www.tidyverse.org/) and try to abide by their 
philosophy. You can install the complete tidyverse by typing the following line 
of code in the R console:

```{r, tidy = TRUE, eval = FALSE}
# Install the tidyverse packages
install.packages("tidyverse")

# Attach the tidyverse packages into the current session
library(tidyverse)
```

We also note the usage of the pipe `%>%` symbol throughout the code of this 
tutorial. The pipe is a way to write a series of operations on an R object, 
e.g. a dataset, in an easy-to-read way. As an example, the operation 
`x %>% f(y)` effectivly means `f(x, y)`. You can read more on the pipe [here](https://cran.r-project.org/web/packages/magrittr/vignettes/magrittr.html).

## Overview of Nightingale blood biomarker data 

The NMR biomarker concentrations are provided in xlsx, csv and tsv formats.
R can read either but in this tutorial we will use the csv format. 

For the purposes of this tutorial we will use an example csv file. 
Download the zipped folder
[here](https://github.com/NightingaleHealth/ggforestplot/blob/master/data-raw/metabolomics_data.zip)
and unzip it. It contains two files, one with metabolomics data and one with 
corresponding clinical data that we will use later on. 

Type the commands below in your R session to load the metabolomics data and view 
the available biomarkers. Mind to put the correct path in the `file` parameter 
below.

```{r, tidy = FALSE, message = FALSE, warning = FALSE, eval = FALSE}
# Read the biomarker concentration file
df_nmr_results <- readr::read_csv(
  # Enter the correct location for your file below
  file = "/path/to/file/12345-Results.csv",
  # Set not only NA but TAG string as <NA> 
  na = c("NA", "TAG"), 
  col_types = cols(.default = col_double(), 
                   Sample_id = col_character())
)
```

```{r, tidy = FALSE, message = FALSE, warning = FALSE, include = FALSE}
# Read the biomarker concentration file
df_nmr_results <- readr::read_csv(
  file = "data/12345-Results.csv",
  # Set not only NA but TAG string as <NA> 
  na = c("NA", "TAG"), 
  col_types = cols(.default = col_double(), 
                   Sample_id = col_character())
)
```

Print the names of all the variables in the dataset for inspection.

```{r, tidy = FALSE}
names(df_nmr_results)
```

The first column, `Sample_id`, contains the sample identifiers. Columns 2 to 19
contain information on different tags that a sample may contain. Explanation on
any tags present in an actual result file is given along with the analysis 
report but here all possible tag columns are provided for demonstarational 
purposes. The rest of the columns correspond to machine readable abbreviations 
of the NMR-quantified blood biomarkers. 

Let us drop the tag columns as they are not used in this demo.

```{r, tidy = FALSE}
df_nmr_results <- 
  df_nmr_results %>% 
  select(-(EDTA_plasma:Unidentified_small_molecule_c))
```

### Rename alternative biomarker names

If you have a Nightingale result file with alternative biomarker names, 
for example `XXL-VLDL-C_%` instead of `XXL_VLDL_C_pct` or `LA/FA` instead of 
`LA_pct`, you may utilize the variable `alternative_ids` in the 
`ggforestplot::df_NG_biomarker_metadata` dataset to convert from one type to the other. 
An example is provided below, where we transform a dataset with alternative
biomarker name (as long as they are found in the 
`ggforestplot::df_NG_biomarker_metadata$alternative_ids` list) to their
`ggforestplot::df_NG_biomarker_metadata$machine_readable_name`.

```{r, tidy = FALSE, eval = FALSE}
# Assume that your data frame, containing alternative biomarker names, is called 
# df_nmr_results_alt_names

alt_names <- 
  names(df_nmr_results_alt_names)

new_names <- 
  alt_names %>% 
  purrr::map_chr(function(id) {
    # Look through the alternative_ids
    hits <-
      purrr::map_lgl(
        df_NG_biomarker_metadata$alternative_names,
        ~ id %in% .
      )

    # If one unambiguous hit, return it.
    if (sum(hits) == 1L) {
      return(df_NG_biomarker_metadata$machine_readable_name[hits])
      # If not found, give a warning and pass through the input.
    } else {
      warning("Biomarker not found: ", id, call. = FALSE)
      return(id)
    } 
  })

# Name the vector with the new names  
names(alt_names) <- new_names

# Rename your result data frame with machine_readable_names 
df_nmr_results_alt_names <- 
  df_nmr_results_alt_names %>% 
  rename(!!alt_names)

```

## Association analysis 

### Join the blood biomarker data with other variables

Next we join the blood biomarker data above with other variables we 
may have, such as patient basic information (e.g. gender, age, e.t.c.) or 
patient outcomes (e.g. a disease event). 

The second dataset you downloaded earlier (from 
[here](https://github.com/NightingaleHealth/ggforestplot/blob/master/data-raw/metabolomics_data.zip)), 
called `clinical_data.csv`, has additional to the NMR information 
corresponding to the same fictional individuals. It has information on gender, 
age, body mass index (BMI) as well as incident T2D diabetes. 

We will join the two datasets using the IDs, i.e. column `Sample_id` in the 
NMR data and column `identifier` in the clinical data. Except for the columns 
having different names in the two files, the IDs themselves are not the 
same either (which is also often the case in real life). `Sample_id` in the 
NMR is a character column with the prefix `ResearchInstitutionProjectLabId_` 
while `identifier` in clinical data is a character consisting of 4 numbers. 

Below we read the clinical data and join the two datasets after a few adjustments.

```{r, tidy = FALSE, eval = FALSE}
# Read the clinical_data.csv data file
df_clinical_data <- readr::read_csv(
  # Enter the correct location for your file below
  file = "/path/to/file/clinical_data.csv") %>%
  # Rename the identifier column to Sample_id as in the NMR result file
  rename(Sample_id = identifier) %>% 
  # Harmonize the id entries in clinical data with the ids in the NMR data 
  mutate(Sample_id = paste0(
    "ResearchInstitutionProjectLabId_", 
    as.numeric(Sample_id)
  ))

```

```{r, tidy = FALSE, include = FALSE}
# Read the clinical_data.csv data file
df_clinical_data <- readr::read_csv(
  file = "data/clinical_data.csv"
) %>%
  # Rename the identifier column to Sample_id as in the NMR result file
  rename(Sample_id = identifier) %>% 
  # Harmonize the id entries in clinical data with the ids in the NMR data 
  mutate(Sample_id = paste0(
    "ResearchInstitutionProjectLabId_", 
    as.numeric(Sample_id)
  ))

```


```{r, tidy = FALSE}
# Inspect the first 10 entries
print(df_clinical_data)

# Join NMR result file with the clinical data using column "Sample_id"
df_full_data <- dplyr::left_join(
  x = df_nmr_results,
  y = df_clinical_data,
  by = "Sample_id"
)
```

### Linear regression

We will first plot the distribution for a specific biomarker to inspect the data
more closely. We choose glycoprotein acetyls (abbrev. GlycA) which reflects the 
amount of N-acetyl groups in circulating glycoproteins, many of which are 
involved in the acute-phase inflammatory response. 

We first add a column to the dataset, marking the subjects as obese or not-obese.
We then plot the GlycA distributions for the two sets as boxplots. 

```{r densityplot, message = FALSE, tidy = FALSE, fig.cap = "GlycA distribution for obese and not-obese subjects"}
df_full_data %>% 
  # Add a column to mark obese/non-obese subjects
  mutate(obesity = ifelse(BMI >= 30, yes = "Obese", no = "Not obese")) %>% 
  # Filter out subjects with missing values (if any)
  filter(!is.na(obesity)) %>% 
  # Box plots for each group
  ggplot(aes(y = GlycA, x = obesity, color = obesity)) +
  geom_boxplot() + 
  # Remove x axis title 
  theme(axis.title.x = element_blank())
```

In the box plot above, the lower, middle and higher hinges correspond to 25%, 
50% and 75% quantiles, respectively. Therefore, we see that the GlycA 
distribution for obese subjects is clearly shifted to higher values as compared 
to non-obese subjects, indicating that this marker is likely positively 
associated with obesity. 

We will now estimate associations of each biomarker to BMI via linear 
regression:

\begin{align*}
y = \beta * x + \alpha
\end{align*}

where the blood biomarker is the outcome, $y$, and BMI is the exposure $x$. 
The association of $x$ with $y$ refers to the beta coefficient ($\beta$).

Below, we use function `ggforestplot::discovery_regression()`, with input parameter
`model` set to `'lm'` to estimate multiple, adjusted, linear associations, for 
all the biomarkers. Note that we log tranform and scale the biomarkers so that 
the magnitude of associations are directly comparable across the different 
biomarkers. (Note: The log-transformation is not, strictly speaking, required 
here: the blood metabolites are in this case the outcome and not the exposure, 
while log-tranformation is done in order to satisfy the assumption of linear 
regression for normal distribution of the residuals.)

```{r, message = FALSE, tidy = FALSE}
# Extract names of NMR biomarkers
nmr_biomarkers <- names(df_nmr_results %>% select(-Sample_id))

# NMR biomarkers here should be 228
stopifnot(length(nmr_biomarkers) == 228)

# Select only variables to be used for the model and collapse to a long data 
# format
df_long <-
  df_full_data %>%
  # Select only model variables
  dplyr::select(nmr_biomarkers, gender, baseline_age, BMI) %>%
  # log-tranform biomarkers
  dplyr::mutate_at(.vars = c(nmr_biomarkers), .funs = dplyr::funs(log1p(.))) %>%
  # Scale biomarkers
  dplyr::mutate_at(.vars = c(nmr_biomarkers), .funs = dplyr::funs(as.numeric(scale(.)))) %>%
  # Collapse to a long data format
  tidyr::gather(key = biomarkerid, value = biomarkervalue, nmr_biomarkers)

# Estimate sex- and age-adjusted associations of metabolite to BMI
df_assoc_per_biomarker_bmi <-
  ggforestplot::discovery_regression(
    df_long = df_long,
    model = "lm",
    formula =
      formula(
       biomarkervalue ~ BMI + factor(gender) + baseline_age
      ),
    key = biomarkerid,
    predictor = BMI
  ) %>% 
  # Join this dataset with the grouping data in order to choose a different 
  # biomarker naming option
  left_join(
    select(
      df_NG_biomarker_metadata, 
      name,
      biomarkerid = machine_readable_name
    ), 
    by = "biomarkerid")

head(df_assoc_per_biomarker_bmi)
```

The data frame `df_assoc_per_biomarker_bmi` above, contains 228 rows, one for each
blood biomarker, and 5 variables (columns): the `biomarkerid` (same as variable 
`machine_readable_name` in `df_NG_biomarker_metadata`) which has the 
biomarker abbreviations in the same format as in the input csv file, the biomarker `name` 
which is a bit more descriptive than `biomarkerid`, and the variables `estimate`, 
`se` and `pvalue` that correspond to the linear regression coefficient $\beta$,
the standard error and the p-value, respectively.

#### Forest plot

Let's now visualize the results. For the purposes of this demo, we will plot a 
selected subset of the biomarkers in a forestplot layout. At the end of 
the tutorial, you will find an example of how to plot associations for all 228 
Nightingale biomarkers in a 2-page pdf  (see also `vignette("ggforestplot")` 
for more details on the usage of `ggforestplot::forestplot()`).

The `ggforestplot` package includes a data frame, called 
`ggforestplot::df_NG_biomarker_metadata`, with metadata on the Nightingale 
blood biomarkers, such as different naming options, descriptions, group/sugroup 
information and units of measurement. We will use the group (or sugroup) 
information in this data frame to decide which groups of biomarkers and in what 
order we want to visualize here.

```{r, tidy = FALSE}
# Display blood biomarker groups
ggforestplot::df_NG_biomarker_metadata %>% 
  pull(group) %>% 
  unique()

# # You may wish, alternatively, to display blood biomarker subgroups and plot 
# # according to that. You can see which subgroups are available in the 
# # grouping data by uncommenting the following lines. In several cases, subgroup
# # is identical to group. 
# ggforestplot::df_NG_biomarker_metadata %>% 
#   pull(subgroup) %>% 
#   unique()

# Choose the groups you want to plot and define the order with which group 
# categories will appear in the plot
group_order <- c(
  "Branched-chain amino acids",
  "Aromatic amino acids",
  "Amino acids",
  "Fluid balance",
  "Inflammation",
  "Fatty acids",
  "Glycerides and phospholipids",
  "Cholesterol"
)
  
# Extract a subset of the df_NG_biomarker_metadata, with the desired group
# order, to set the order of biomarkers in the forestplot later on
df_with_groups <- 
  ggforestplot::df_NG_biomarker_metadata %>% 
  # Select subset of variables
  select(name = name,
         group) %>% 
  # Filter and arrange for the wanted groups
  filter(group %in% group_order) %>%
  arrange(factor(group, levels = group_order))

```

##### Statistical significance for multiple testing

We'd also like to add to the forrestplot a Bonferroni correction to account for 
multiple testing. Here we have a comparison of 228 biomarkers. If we suppose the
common significance threshold $\alpha = 0.05$, the Bonferroni correction for each 
individual hypothesis, assuming the 228 tests are independent, is 
$\alpha = 0.05 / 228 \approx 0.0002$. However, for biologically correlated 
measures this correction is too strict; Here, instead of correcting for the 
total number of biomarkers we will use the number of principal components 
that explain 99% of the variance in the data. 

```{r, tidy = FALSE}
# Perform principal component analysis on metabolic data
df_pca <- 
  df_full_data %>% 
  select(Total_C:S_HDL_TG_pct) %>% 
  nest() %>% 
  mutate(
    # Perform PCA on the data above, after scaling and centering to 0 
    pca = map(data, ~ stats::prcomp(.x, center = TRUE, scale = TRUE)),
    # Augment the original data with columns containing each observation's 
    # projection into the PCA space. Each PCA-space dimension is signified 
    # with the .fitted prefix in its name 
    pca_aug = map2(pca, data, ~broom::augment(.x, data = .y))
  )

# Estimate amount of variance explained by each principal component
df_pca_variance <- 
  df_pca %>% 
  unnest(pca_aug) %>% 
  # Estimate variance for the PCA projected variables
  summarize_at(.vars = vars(starts_with(".fittedPC")), .funs = funs(var)) %>% 
  # Gather data in a long format 
  gather(key = PC, value = variance) %>% 
  # Estimate cumulative normalized variance
  mutate(cumvar = cumsum(variance / sum(variance)),
         PC = str_replace(PC, ".fitted", ""))

# Find number of principal components that explain 99% 
pc_99 <- 
  df_pca_variance %>% 
  filter(cumvar <= 0.99) %>% 
  nrow()

print(pc_99)
```

Therefore, our significance threshold here will be $\alpha = 0.05 / 49 \approx 0.001$

Below we plot the results. In the forestplot function, our main input is the 
data frame `df_assoc_per_biomarker_bmi`, while we use the previously constructed
data frame `df_with_groups` and its variable `group` to impose the grouping and 
the order of biomarkers in the plot. For the statistical significance, we input 
the significance threshold as the parameter `psignif = 0.001` and we define 
explicitly the variable name in `df_assoc_per_biomarker_bmi` that contains the 
p-values of the linear regression, in this case the column pvalue. 

```{r forestplot, tidy = FALSE,  fig.height = 13}
# Join the association data frame with group data
df_to_plot <-
  df_assoc_per_biomarker_bmi %>%
  # use right_join, with df_grouping on the right, to preserve the order of 
  # biomarkers it specifies. 
  dplyr::right_join(., df_with_groups, by = "name") 

# Draw a forestplot of cross-sectional, linear associations.
ggplot_multi <-
  df_to_plot %>%
  nest(-group, .key = "data") %>%
  # Apply forestplot to each group 
  mutate(
    gg_groups = purrr::map2(
      data, group, ~ forestplot(
        df = .x,
        pvalue = pvalue,
        psignif = 0.001,
        xlab = "1-SD increment in biomarker concentration\nper 1-SD increment in BMI",
        title = .y
      ) +
        ggplot2::coord_cartesian(xlim = c(-0.3, 0.4))
    ),
    # Optional: remove x-axis and legend for all plots except the bottom one
    gg_groups = ifelse(
      test = row_number() != n(),
      yes =
        purrr::map(gg_groups, ~ . +
          theme(
            axis.text.x = element_blank(),
            axis.title.x = element_blank(),
            axis.ticks.x = element_blank(),
            plot.margin = unit(c(1, 2, 1, 2), "mm")
          ) +
          ggplot2::theme(legend.position = "none")),
      no = gg_groups
    ),
    rel_heights = purrr::map(
      data,  ~ nrow(.) 
    ) %>% unlist()
  )

patchwork::wrap_plots(
  ggplot_multi$gg_groups,
  ncol = 1, 
  heights = ggplot_multi$rel_heights
)
```

The figure shows that BMI is significantly associated with several of the 
plotted blood biomarkers. Specifically, higher values of branched chain amino 
acids, aromatic amino acids omega-6 and glycoprotein acetylation are significantly 
associated with obesity, as has been previously seen in [Würtz P et al. 
Metabolic Signatures of Adiposity in Young Adults: Mendelian Randomization Analysis and Effects of Weight Change., 
PLoS Med. 2014.](https://journals.plos.org/plosmedicine/article?id=10.1371/journal.pmed.1001765)

### Cox proportional hazards regression

Similar analysis may be performed for other phenotypic traits. Two other very 
common regression approaches in epidemiology are logistic regression for 
studying the association to binary outcomes and Cox proportional hazards for 
time-to-event outcomes. 

In similar spirit as above, we utilize `ggforestplot::discovery_regression()` to 
demonstrate an example of fitting Cox proportional hazards in all of the biomarkers 
to estimate the gender-, age- and BMI- adjusted hazard ratios for type 2 diabetes.

```{r, message = FALSE, tidy = FALSE}
# Select only variables to be used for the model and collapse to a long data 
# format
df_long <-
  df_full_data %>%
  # Select only model variables
  dplyr::select(nmr_biomarkers, gender, baseline_age, BMI, age_at_diabetes, incident_diabetes) %>%
  # log-tranform biomarkers
  dplyr::mutate_at(.vars = c(nmr_biomarkers), .funs = dplyr::funs(log1p(.))) %>%
  # Scale biomarkers
  dplyr::mutate_at(.vars = c(nmr_biomarkers), .funs = dplyr::funs(as.numeric(scale(.)))) %>%
  # Collapse to a long data format
  tidyr::gather(key = biomarkerid, value = biomarkervalue, nmr_biomarkers)

# Estimate sex-adjusted associations of metabolite to T2D
# Notice that parameter model below is set to 'coxph'
df_assoc_per_biomarker_diab <-
  discovery_regression(
    df_long = df_long, 
    model = "coxph",
    formula =
      formula(
        survival::Surv(
          time = baseline_age,
          time2 = age_at_diabetes,
          event = incident_diabetes
        ) ~ biomarkervalue + factor(gender) + BMI
      ),
    key = biomarkerid,
    predictor = biomarkervalue
  ) %>% 
  # Join this dataset with the grouping data in order to choose a different 
  # biomarker naming option
  left_join(
    select(
      df_NG_biomarker_metadata, 
      name,
      biomarkerid = machine_readable_name
    ), 
    by = "biomarkerid")

head(df_assoc_per_biomarker_diab)
```

Plot results for fatty acids.

```{r, tidy = FALSE,  fig.height = 6}
# Filter df_NG_biomarker_metadata for only fatty acids
df_grouping <-
  df_NG_biomarker_metadata %>% 
  filter(group %in% "Fatty acids") 

# Join the association data frame with group data
df <-
  df_assoc_per_biomarker_diab %>%
  # use right_join, with df_grouping on the right, to preserve the order of 
  # biomarkers it specifies. 
  dplyr::right_join(., df_grouping, by = "name") 

# Draw a forestplot of time-to-event associations for t2d. 
ggforestplot::forestplot(
  df = df, 
  name = name,
  se = se,
  pvalue = pvalue,
  psignif = 0.001,
  xlab = "Hazards ratio for incident type 2 diabetes (95% CI)\nper 1−SD increment in metabolite concentration",
  title = "Fatty acids and risk of future T2D",
  logodds = TRUE
) 
```

Notice that the main difference in the latter forestplot as compared to the 
forestplot for linear associations above, is parameter `logodds = TRUE`. In 
this case, the `beta` values, here log hazard ratios, are exponentiated inside
the forestplot to obtain hazard ratios and plotted in a logarithmic scale. 
The confidence intervals for the odds ratios are estimated using the standard 
errors of the log hazard ratios, as follows 
$\text{CI}_\text{low} = \exp(\beta - 0.95 * \text{SE})$ and 
$\text{CI}_\text{high} = \exp(\beta - 0.95 * \text{SE})$. If you wish to use 
some confidence interval other than the default 95%, you may specify this in the 
parameter `ci` of the function.

### A forestplot for all Nightingale blood biomarkers

Finally, the `ggforestplot` package offers a custom function that plots and 
prints in a 2-page pdf file all Nightingale blood biomarkers, namely 
`plot_all_NG_biomarkers()`. It's usage is straightforward.

```{r, tidy = FALSE, eval = FALSE}
# Plot in all biomarkers in a two-page pdf file
plot_all_NG_biomarkers(
  df = df_assoc_per_biomarker_bmi, 
  machine_readable_name = biomarkerid,
  name = name, 
  estimate = estimate, 
  se = se, 
  pvalue = pvalue, 
  xlab = "1-SD increment in cardiometabolic trait\nper 1-SD increment in biomarker concentration",
  filename = "all_ng_associations_bmi.pdf"
)
```

```{r, tidy = FALSE, include = FALSE, eval = FALSE}
# ------------> Evaluate this only when you want to refresh the pdf plots in 
# ------------> figures/ Don't update them everytime if not necessary as git 
# ------------> saves multiple copies. 
# Plot in all biomarkers in a two-page pdf file
plot_all_NG_biomarkers(
  df = df_assoc_per_biomarker_bmi, 
  machine_readable_name = biomarkerid,
  name = name, 
  estimate = estimate, 
  se = se, 
  pvalue = pvalue, 
  xlab = "1-SD increment in cardiometabolic trait\nper 1-SD increment in biomarker concentration",
  filename = "figures/all_ng_associations_bmi.pdf"
)
```

You may view the output of this function [here](https://github.com/NightingaleHealth/ggforestplot/blob/master/vignettes/figures/all_ng_associations_bmi.pdf)

## Final remarks

The purpose of this demo is to familiarize the user with the Nightingale Health 
biomarker dataset and to showcase simple association analysis using linear and 
Cox proportional hazards regression. 

Further details on data analysis approaches may be found in the following 
example publications.

## References 

* [Akbaraly T, et al. Association of circulating metabolites with 
healthy diet and risk of cardiovascular disease: analysis of two cohort studies. 
Sci Rep. 2018; 8: 8620](https://www.ncbi.nlm.nih.gov/pmc/articles/PMC5988716/)

* [Würtz P, et al. Metabolite profiling and cardiovascular event risk: a prospective 
study of 3 population-based cohorts. Circulation. 2015 Mar 3;131(9):774-85.](https://www.ncbi.nlm.nih.gov/pubmed/25573147)

* [Würtz P, et al. Metabolomic Profiling of Statin Use and Genetic Inhibition of HMG-CoA Reductase, J Am Coll Cardiol. 2016 Mar 15;67(10):1200-1210](https://www.sciencedirect.com/science/article/pii/S0735109716003223?via%3Dihub)

